Enforced Invariant Confluence

### 2018-02-15 doc/paper_redux/iconfluence.tex
Minor style adjustments.

\section{\Iconfluence{}}
A \emph{distributed object} is a triple $(S, s_0, \join)$ where $S$ is a set of
states, $s_0 \in S$ is a designated start state, and $\join: S \times S \to S$
is a commutative binary merge operator. A \emph{transaction} $t: S \to S$ is a
function that maps one state to another. An \emph{invariant} $I: S \to
\set{\text{true}, \text{false}}$ is a predicate on states. For example,
$(\nats, +)$ is a distributed object, $t(x) = 2x$ is a transaction, and $I(x) =
x \geq 0$ is an invariant.

@@

\subsection{Graph-Based}
The graph-based approach is most similar to the model used by Bailis et al.\
in~\cite{bailis2014coordination}. We are given a directed acyclic graph in
which vertices can have an arbitrary number of children but at most two
parents. The vertices are labelled with states, and the edges are either
labelled with transactions or are unlabelled if they correspond to a join. The
graph is really just an alternate way of representing an execution in the
process-based model, but with duplicate states collapsed into a single vertex.
As with the process-based model, we say $T$ is \Iconfluent{} if the join of any
two invariant satisfying states with invariant satisfying ancestors is
guaranteed to satisfy the invariant.

>>>>

\section{\Iconfluence{}}
A \emph{distributed object} is a triple $(S, s_0, \join)$ where $S$ is a set of
states, $s_0 \in S$ is a designated start state, and $\join: S \times S \to S$
is a commutative binary merge operator that we call join. A \emph{transaction}
$t: S \to S$ is a function that maps one state to another. An \emph{invariant}
$I: S \to \set{\text{true}, \text{false}}$ is a predicate on states. For
example, $(\nats, +)$ is a distributed object, $t(x) = 2x$ is a transaction,
and $I(x) = x \geq 0$ is an invariant.

@@

\subsection{Graph-Based}
The graph-based approach is most similar to the model used by Bailis et al.\
in~\cite{bailis2014coordination}. We are given a directed acyclic graph in
which vertices can have an arbitrary number of children but at most two
parents. The vertices are labelled with states, and the edges are either
labelled with transactions or are unlabelled if they correspond to a join. The
graph is really just an alternate way of representing an execution in the
process-based model, but with duplicate states collapsed into a single vertex.
As with the process-based model, we say that $T$ is \Iconfluent{} if the join
of any two invariant satisfying states with invariant satisfying ancestors is
guaranteed to satisfy the invariant.
